Figure 5 - IP-MS

### 2024-08-07 ms_figure_5_ipms.Rmd
Minor reorganisations, Fig5

makeInteractorSummary(sce = sce150, baitdata = baitdata_150, adjp_cutoff = adjpThreshold,
                      logfc_cutoff = log2fcThreshold, idmap = idmap, 
                      baits_to_keep = baitclass$Gene_name[baitclass$class != "nobait"],
                      tbl_title = "150 mM, strict cutoff") |>
    dplyr::full_join(
        makeInteractorSummary(sce = sce500, baitdata = baitdata_500, adjp_cutoff = adjpThreshold,
                              logfc_cutoff = log2fcThreshold, idmap = idmap, 
                              baits_to_keep = baitclass$Gene_name[baitclass$class != "nobait"],
                              tbl_title = "500 mM, strict cutoff")
    ) |> 
    dplyr::full_join(
        makeInteractorSummary(sce = sce150, baitdata = baitdata_150_loose, adjp_cutoff = adjpThresholdLoose,
                              logfc_cutoff = log2fcThreshold, idmap = idmap, 
                              baits_to_keep = baitclass$Gene_name[baitclass$class != "nobait"],
                              tbl_title = "150 mM, lenient cutoff")
    ) |>
    dplyr::full_join(
        makeInteractorSummary(sce = sce500, baitdata = baitdata_500_loose, adjp_cutoff = adjpThresholdLoose,
                              logfc_cutoff = log2fcThreshold, idmap = idmap, 
                              baits_to_keep = baitclass$Gene_name[baitclass$class != "nobait"],
                              tbl_title = "500 mM, lenient cutoff")
    ) |>
    kbl() |>
    kable_styling()
```

@@

hm1b <- Heatmap(baitdata_150$mat, 
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                col = makeHeatmapCol(stringency = "high"), 
                border = TRUE, 
                border_gp = gpar(lwd = 0.5),
                name = "Mod.\nt-stat.", 
                na_col = binary_heatmap_colors["FALSE"],
                column_title = paste(c("150 mM NaCl IP-MS", rep(" ", 45)), collapse = ""),
                row_title = "Transcription factors",
                column_title_gp = gpar(fontsize = fl + 3, fontface = "bold"),
                row_title_gp = gpar(fontsize = fl),
                column_names_gp = gpar(fontsize = fs),
                row_names_gp = gpar(fontsize = fs),
                show_row_names = FALSE, show_column_names = FALSE,
                use_raster = FALSE, show_heatmap_legend = TRUE, 
                left_annotation = makeComplexAndDBDAnnotation(
                    baitdata_150$mat, 
                    complexes[c("MBF transcription complex", 
                                "CCAAT-binding factor complex",
                                "Atf1-Pcr1")],
                    dbd = dbd, 
                    idmap = idmap),
                top_annotation = makeTFIntAnnotation(baitdata_150), 
                bottom_annotation = makeColLabels(baitdata_150_loose$mat, 
                                                  c("Ntu1_plate", "Ntu2_plate", 
                                                    "Esc1_tube", "SPAC3F10.12c_plate"), fl),
                      width = unit(w_ipmsHm, "mm") / 1.05, # heatmap body width
                heatmap_height = unit(h_ipmsHm / 1.6, "mm"),
                heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                            border = "gray10",
                                            border_gp = gpar(lwd = 0.5)))

@@

legend_bait_1 <- grid.grabExpr(
    hm1b <- ComplexHeatmap::draw(lgd_complex),
    width = w_ipmsHm, height = h_ipmsHm / 8
)
legend_bait_2 <- grid.grabExpr(
    hm1b <- ComplexHeatmap::draw(lgd_dbd),
    width = w_ipmsHm, height = h_ipmsHm / 8
)
```

```{r}
pie_bait_150 <- makePie(baitdata = baitdata_150,
                        title = "150 mM NaCl\nstrict cutoff")
```

@@

```{r}
pie_bait_150_loose <- makePie(baitdata = baitdata_150_loose, 
                              title = "150 mM NaCl\nlenient cutoff")
```

@@

```{r}
pie_bait_500 <- makePie(baitdata = baitdata_500, 
                        title = "500 mM NaCl\nstrict cutoff")

@@

The pie charts below display the number of observed within- and between-DBD 
family interactions under different salt conditions and using different 
thresholds for identifying interactions. The black arc indicate the  
fraction of within-DBD family interactions expected by chance.

@@

```{r tstat-150-vs-500}
#| fig.width: 6
#| fig.height: 7
#| message: false

@@

## Supplementary plot - tube vs plate t-statistics for Atf1 pull-down

@@

## Supplementary plot - Adn2 vs complement volcano plot

# Pho7 volcano plot

```{r}
#| warning: false

@@

## Supplementary plot - histone proteins t-stats

@@

## Get all t-statistics and visualize
res500 <- .getTestCols(sce500, adjp_cutoff = 0.01, logfc_cutoff = 1)
histones <- res500$tstat[c("Hta1", "Htb1", "Hht2", "Hhf2"), ]
colnames(histones) <- .getProteinNameFromComparison(colnames(histones))
histones <- histones[, colnames(histones) != "Untagged"]
histones <- t(histones)
hmhistones <- Heatmap(histones, 
                      cluster_rows = TRUE, 
                      cluster_columns = FALSE, 
                      col = circlize::colorRamp2(
                          breaks = seq(1.5, 13.0, length.out = 64),
                          colors = colorRampPalette(
                              binary_heatmap_colors[c("FALSE", "TRUE")])(64)),
                      border = TRUE, 
                      border_gp = gpar(lwd = 0.5),
                      name = "Mod.\nt-stat.",
                      na_col = binary_heatmap_colors["FALSE"],
                      column_names_gp = gpar(fontsize = fl),
                      row_names_gp = gpar(fontsize = fs),
                      show_row_names = TRUE, 
                      show_column_names = TRUE, 
                      use_raster = FALSE,
                      show_heatmap_legend = TRUE, 
                      width = unit(w_ipmsHm / 1.5, "mm"), 
                      heatmap_height = unit(1.3 * h_ipmsHm, "mm"),
                      column_title_gp = gpar(fontsize = ft),
                      heatmap_legend_param = list(
                          title_gp = gpar(fontsize = fl),
                          border = "gray10",
                          border_gp = gpar(lwd = 0.5)
                      ))
set.seed(42L)
hm_histones <- grid.grabExpr(
    hmrad <- draw(hmhistones, merge_legend = TRUE,
                 heatmap_legend_side = "right",
                 annotation_legend_side = "right"),
    width = w_ipmsHm / 1.5, height = 1.3 * h_ipmsHm
)
plot_grid(hm_histones)
```

@@

## Supplementary Figure 5

```{r}
#| label: SuppFig5
#| fig.width: 10
#| fig.height: 10
#| warning: false

cowplot::plot_grid(
    cowplot::plot_grid(
        pies, 
        adn2volc, 
        ncol = 1
    ),
    hm_histones,
    nrow = 1
)
```

>>>>

makeInteractorSummary(sce = sce150, baitdata = baitdata_150, adjp_cutoff = adjpThreshold,
                      logfc_cutoff = log2fcThreshold, idmap = idmap, 
                      baits_to_keep = baitclass$Gene_name[baitclass$class != "nobait"],
                      tbl_title = "150 mM, strict cutoff") |>
    dplyr::full_join(
        makeInteractorSummary(sce = sce500, baitdata = baitdata_500, adjp_cutoff = adjpThreshold,
                              logfc_cutoff = log2fcThreshold, idmap = idmap, 
                              baits_to_keep = baitclass$Gene_name[baitclass$class != "nobait"],
                              tbl_title = "500 mM, strict cutoff"),
        by = join_by(Aspect)
    ) |> 
    dplyr::full_join(
        makeInteractorSummary(sce = sce150, baitdata = baitdata_150_loose, adjp_cutoff = adjpThresholdLoose,
                              logfc_cutoff = log2fcThreshold, idmap = idmap, 
                              baits_to_keep = baitclass$Gene_name[baitclass$class != "nobait"],
                              tbl_title = "150 mM, lenient cutoff"),
        by = join_by(Aspect)
    ) |>
    dplyr::full_join(
        makeInteractorSummary(sce = sce500, baitdata = baitdata_500_loose, adjp_cutoff = adjpThresholdLoose,
                              logfc_cutoff = log2fcThreshold, idmap = idmap, 
                              baits_to_keep = baitclass$Gene_name[baitclass$class != "nobait"],
                              tbl_title = "500 mM, lenient cutoff"),
        by = join_by(Aspect)
    ) |>
    kbl() |>
    kable_styling()
```

@@

hm1b <- Heatmap(baitdata_150$mat, 
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                col = makeHeatmapCol(stringency = "high"), 
                border = TRUE, 
                border_gp = gpar(lwd = 0.5),
                name = "Mod.\nt-stat.", 
                na_col = binary_heatmap_colors["FALSE"],
                column_title = paste(c("150 mM NaCl IP-MS", rep(" ", 45)), collapse = ""),
                row_title = "Transcription factors",
                column_title_gp = gpar(fontsize = fl + 3, fontface = "bold"),
                row_title_gp = gpar(fontsize = fl),
                column_names_gp = gpar(fontsize = fs),
                row_names_gp = gpar(fontsize = fs),
                show_row_names = FALSE, show_column_names = FALSE,
                use_raster = FALSE, show_heatmap_legend = TRUE, 
                left_annotation = makeComplexAndDBDAnnotation(
                    baitdata_150$mat, 
                    complexes[c("MBF transcription complex", 
                                "CCAAT-binding factor complex",
                                "Atf1-Pcr1")],
                    dbd = dbd, 
                    idmap = idmap),
                top_annotation = makeTFIntAnnotation(baitdata_150), 
                bottom_annotation = makeColLabels(baitdata_150$mat, 
                                                  c("Ntu1_plate", "Ntu2_plate", 
                                                    "Esc1_tube", "SPAC3F10.12c_plate"), fl),
                width = unit(w_ipmsHm, "mm") / 1.05, # heatmap body width
                heatmap_height = unit(h_ipmsHm / 1.6, "mm"),
                heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                            border = "gray10",
                                            border_gp = gpar(lwd = 0.5)))

@@

legend_bait_1 <- grid.grabExpr(
    hm1bl1 <- ComplexHeatmap::draw(lgd_complex),
    width = w_ipmsHm, height = h_ipmsHm / 8
)
legend_bait_2 <- grid.grabExpr(
    hm1bl2 <- ComplexHeatmap::draw(lgd_dbd),
    width = w_ipmsHm, height = h_ipmsHm / 8
)
```

@@

@@

The pie charts below display the number of observed within- and between-DBD 
family interactions under different salt conditions and using different 
thresholds for identifying interactions. The black arc indicate the  
fraction of within-DBD family interactions expected by chance, given the 
observed number of elements in each of the families.

```{r}
#| label: make-pies

pie_bait_150 <- makePie(baitdata = baitdata_150,
                        title = "150 mM NaCl\nstrict cutoff")

pie_bait_150_loose <- makePie(baitdata = baitdata_150_loose, 
                              title = "150 mM NaCl\nlenient cutoff")

pie_bait_500 <- makePie(baitdata = baitdata_500, 
                        title = "500 mM NaCl\nstrict cutoff")

@@

@@

```{r}
#| label: tstat-150-vs-500
#| fig.width: 6
#| fig.height: 7
#| message: false

@@

## Tube vs plate t-statistics for Atf1 pull-down

@@

## Adn2 vs complement volcano plot

```{r}
#| label: adn2-volc
#| warning: false

@@

## Histone proteins t-stats

@@

## Get all t-statistics and visualize
res500 <- .getTestCols(sce500, adjp_cutoff = 0.01, logfc_cutoff = 1)
histones <- res500$tstat[c("Hta1", "Htb1", "Hht2", "Hhf2"), ]
colnames(histones) <- .getProteinNameFromComparison(colnames(histones))
histones <- histones[, colnames(histones) != "Untagged"]
histones <- t(histones)
hmhistones <- Heatmap(histones, 
                      cluster_rows = TRUE, 
                      cluster_columns = FALSE, 
                      col = makeHeatmapCol(stringency = "low"), 
                      border = TRUE, 
                      border_gp = gpar(lwd = 0.5),
                      name = "Mod.\nt-stat.",
                      na_col = binary_heatmap_colors["FALSE"],
                      column_names_gp = gpar(fontsize = fl),
                      row_names_gp = gpar(fontsize = fs),
                      show_row_names = TRUE, 
                      show_column_names = TRUE, 
                      use_raster = FALSE,
                      show_heatmap_legend = TRUE, 
                      width = unit(w_ipmsHm / 1.5, "mm"), 
                      heatmap_height = unit(1.3 * h_ipmsHm, "mm"),
                      column_title_gp = gpar(fontsize = ft),
                      heatmap_legend_param = list(
                          title_gp = gpar(fontsize = fl),
                          border = "gray10",
                          border_gp = gpar(lwd = 0.5)
                      ))
set.seed(42L)
hm_histones <- grid.grabExpr(
    hmrad <- draw(hmhistones, merge_legend = TRUE,
                 heatmap_legend_side = "right",
                 annotation_legend_side = "right"),
    width = w_ipmsHm / 1.5, height = 1.3 * h_ipmsHm
)
plot_grid(hm_histones)
```

@@

## Supplementary figure

```{r}
#| label: suppFig5
#| fig.width: 10
#| fig.height: 10
#| warning: false

cowplot::plot_grid(
    cowplot::plot_grid(
        pies, 
        adn2volc, 
        ncol = 1,
        labels = c("A", "B")
    ),
    hm_histones,
    nrow = 1,
    labels = c("", "C")
)
```
